Do we need detailed demographic data to forecast plant population responses to climate change?

### 2015-05-20 manuscript/manuscript.Rmd
updates figure 4 in ms

```{r figure_4, dependson="plot-options", fig.cap="Proportional change in species' mean cover caused by a 1% increase in observed precipitation, temperature, or both as predicted by the individual-based IPM and the aggregate-based QBM. Note that the change for POSE due to a precipitation increase predicted by the QBM is almost zero and so does not show up in the figure. Labels on x-axis refer to: 'ppt' = 1% increase in mean precipitation; 'temp' = 1% increase in mean temperature; 'ppt + temp' = 1% increase in mean precipitation and mean temperature.", fig.width=6.5, fig.height=6, cache=FALSE, results='hide'}
climBase <- readRDS("../montana/quadBM/simulations/baselineSimulationQBM.rds")
climPpt <- readRDS("../montana/quadBM/simulations/pptChangeSimulationQBM.rds")
climTemp <- readRDS("../montana/quadBM/simulations/tempChangeSimulationQBM.rds")
climBoth <- readRDS("../montana/quadBM/simulations/temp-pptChangeSimulationQBM.rds")
climBase$sim <- rep("AObserved", nrow(climBase)) 
climPpt$sim <- rep("BPrecipitation", nrow(climBase)) 
climTemp$sim <- rep("CTemperature", nrow(climBase)) 
climBoth$sim <- rep("DBoth", nrow(climBase)) 
climSimsQBM <- rbind(climBase, climPpt, climTemp, climBoth)
qbm_means <- ddply(climSimsQBM, .(species, sim), summarise,
                   avg_cover = mean(cover))
tmpid <- which(qbm_means$sim=="AObserved")
diffs <- list()
for(i in 1:length(tmpid)){
  obs <- qbm_means[tmpid[i],"avg_cover"]
  diffs[[i]] <- (rep(obs,3) - qbm_means[(tmpid[i]+1):(tmpid[i]+3), "avg_cover"])/rep(obs,3)
}
names(diffs) <- unique(qbm_means$species)
diff_df <- melt(as.data.frame(diffs))
diff_df$sim <- rep(c("pptChange", "tempChange", "temppptChange"),4)
diff_df$type <- rep("QBM", nrow(diff_df))

ipm_diffs <- readRDS("../montana/ipm/simulations/results/ipm_climatesims_percdiffs.rds")
ipm_diffs$type <- rep("IPM", nrow(ipm_diffs))

diff_df <- rbind(diff_df, ipm_diffs)

>>>>

```{r figure_4, dependson="plot-options", fig.cap="Proportional change in species' mean cover caused by a 1% increase in observed precipitation, temperature, or both as predicted by the individual-based IPM and the aggregate-based QBM. Note that the change for POSE due to a precipitation increase predicted by the QBM is almost zero and so does not show up in the figure. Labels on x-axis refer to: 'ppt' = 1% increase in mean precipitation; 'temp' = 1% increase in mean temperature; 'ppt + temp' = 1% increase in mean precipitation and mean temperature.", fig.width=6.5, fig.height=6, cache=FALSE, results='hide'}
qbm_diffs <- readRDS("../montana/quadBM/simulations/results/qbm_climatesims_percdiffs.rds")
qbm_diffs$type <- rep("QBM", nrow(qbm_diffs))
ipm_diffs <- readRDS("../montana/ipm/simulations/results/ipm_climatesims_percdiffs.rds")
ipm_diffs$type <- rep("IPM", nrow(ipm_diffs))

diff_df <- rbind(qbm_diffs, ipm_diffs)
